\documentclass[a4paper,10pt]{article}

\usepackage[margin=1.8cm]{geometry}
\usepackage{hyperref}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{xcolor}
\usepackage{fontawesome5}
\usepackage{array}
\usepackage{tabularx}

% ---- Colours ----
\definecolor{accent}{HTML}{1f6feb}
\definecolor{muted}{HTML}{555555}

% ---- Hyperlink setup ----
\hypersetup{
  colorlinks=true,
  urlcolor=accent,
  linkcolor=accent
}

% ---- Section styling ----
\titleformat{\section}
  {\large\bfseries\color{accent}}
  {}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{10pt}{6pt}

\setlength{\parindent}{0pt}
\pagestyle{empty}

% ---- Helper: CV Item ----
\newcommand{\cvitem}[4]{%
  \textbf{#1} \hfill \textit{\color{muted}#2} \\
  \textit{#3} \hfill \color{muted}#4 \\[2pt]
}

\begin{document}

% ============================
%           HEADER
% ============================
\begin{center}
  {\LARGE\bfseries Karandeep Singh}\\[4pt]
  \color{muted}
  \faEnvelope\ \href{mailto:karandeep6595@gmail.com}{karandeep6595@gmail.com} \quad
  \faPhone\ \href{tel:+4915215416455}{+49 152 1541 6455} \quad
  \faMapMarker*\ Berlin, Germany \\[2pt]
  \faGithub\ \href{https://github.com/karandeep6595-maker}{github.com/karandeep6595}
\end{center}

\vspace{6pt}

% ============================
%           ABOUT
% ============================
\section{Profile}

Motivated Computer Science undergraduate at Gisma University of Applied Sciences, Berlin.
Experienced in Python programming, database design, and data structures. A collaborative
team player with strong communication skills across multiple languages, committed to
producing clear and well-structured technical work.

% ============================
%         EDUCATION
% ============================
\section{Education}

\cvitem{BSc Computer Science}{2023 -- Present}
       {Gisma University of Applied Sciences}{Berlin, Germany}
Relevant modules: Introduction to Python, Databases, Data Structures \& Algorithms (DSA)

\vspace{6pt}

\cvitem{Higher Secondary Certificate (PCM + CS)}{Completed prior to 2023}
       {Physics, Chemistry, Mathematics \& Computer Science}{}

% ============================
%      TECHNICAL SKILLS
% ============================
\section{Technical Skills}

\begin{tabular}{@{}p{3.5cm} p{11cm}}
  \textbf{Programming}    & Python (entry level), SQL \\
  \textbf{CS Concepts}    & Data Structures, Algorithms, Relational Databases \\
  \textbf{Tools}          & Git, GitHub, GitHub Pages, \LaTeX \\
  \textbf{Web}            & HTML, CSS (static sites) \\
\end{tabular}

% ============================
%        LANGUAGES
% ============================
\section{Languages}

\begin{tabular}{@{}p{3.5cm} p{11cm}}
  \textbf{English}  & Fluent \\
  \textbf{Hindi}    & Native \\
  \textbf{Punjabi}  & Native \\
  \textbf{German}   & Basic (A1/A2) \\
\end{tabular}

% ============================
%         PROJECTS
% ============================
\section{Projects}

\textbf{CS Portfolio Website} \hfill \href{https://github.com/karandeep6595}{github.com/karandeep6595}\\
A personal computer science portfolio hosted on GitHub Pages. Built with HTML and CSS,
featuring a CV (this document) and a showcase of technical exercises.

\vspace{6pt}
\textbf{Python Programming Exercises}\\
Entry-level Python programs covering control flow, functions, lists, and file I/O,
developed as part of the B201 Computer Science Lab module.

\vspace{6pt}
\textbf{Database Design \& SQL Queries}\\
ER diagram design, relational schema normalisation, and SQL query writing
practised in the Databases module.

\vspace{6pt}
\textbf{Data Structures Implementations}\\
Python implementations of linked lists, stacks, queues, and sorting algorithms
completed in the DSA module.

% ============================
%       SOFT SKILLS
% ============================
\section{Soft Skills}

\begin{itemize}[leftmargin=*, itemsep=2pt]
  \item \textbf{Teamwork \& Collaboration} -- comfortable working in group settings,
        contributing to shared goals and coordinating tasks across team members.
  \item \textbf{Communication} -- able to explain technical concepts clearly in
        English, Hindi, and Punjabi; developing German language ability.
  \item \textbf{Self-awareness} -- actively managing workload through structured
        planning and task prioritisation to address challenges with time management.
\end{itemize}

% ============================
%          INTERESTS
% ============================
\section{Interests}

Computer Science fundamentals \textbullet\ Software development \textbullet\
Open-source tools \textbullet\ Multilingual communication

\vfill
{\footnotesize\color{muted} Last updated: 2025}

\end{document}